\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-23 root.tex
fix transition to summary and other minor changes

We first describe the architecture of our system in Sec. \ref{sec:systemarchirecture}.
We also describe other subsystems that our system needs to work with, and planned stops.
Section \ref{sec:pathmanager} describes the high level Path Manager that calls the trajectory planner as necessary to 
exhibit reactive behavior and stop for pedestrians that may appear on the road.
In Section \ref{sec:trajectoryplanning}, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies maximum velocity, acceleration and jerk constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
We then conclude and discuss future extensions.
% tracking

@@

We assume that we have access to a path planner.
For example, this can be a service similar to Google Maps except that instead of road level route, it provides lane level route. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a high resolution digital map with lane centers, stop signs, crosswalk geometry, and turning curves at intersections.
The destination is manually input into the system by the passengers.
Using the path planner, we obtain a path along lane centers from the vehicle's current location (computed by the navigation filter) to the destination.
This plan is output as a set of global waypoints, with the waypoints corresponding to stop signs flagged.
This same map database is used to search for stop signs and provide their locations.

@@

We also have an In-Out Algorithm implemented via polygon intersection that can be used to ignore “safe” pedestrians
Pedestrians that are on sidewalks, off-path crosswalks, and behind planned stops as shown in Figure \ref{fig:intersect} can be considered ``safe'' and are ignored.
This is done by searching the same map database used for path planning.
Remaining pedestrians pose collision risk and the vehicle needs to reactively slow down or stop for them.
This is accomplished by sending stop message with pedestrian locations to the path manager.

@@

The task of Trajectory Planning is to take a 2 dimensional (horizontal plane) set of waypoints from the Path Manager, and compute a series of constant jerk intervals for motion along the length of the path.
This trajectory must be time optimal yet still fall within constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

@@

The segmentation process proceeds as follows:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where 
%$v_m$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
initial/final speeds, speed limit, peak acceleration and jerk 
are found for every point in the given subpath.
  \item \emph{Clustering}, in which subpath points are grouped sequentially and the segment boundaries are determined..
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described in Section \ref{sec:jerkprofiles} may be applied to each of the segments so that a plan of jerk vs. time may be generated.

@@

% need better notation here.
In the consolidation step, a single set of 
%$\mathbf{g}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
initial/final speeds, speed limit, peak acceleration and jerk 
must be calculated for each segment using the values corresponding to each of the waypoints which comprise the segment in question.
The minimum of scalar across all constituent points is chosen.
While not time optimal, it does ensure that no constraints are violated while still keeping the number of total segments low.
In the present example, this means that in the straight portions of the subpath $v_m = SL$ and in the curves $v_m$ is set to the value required to obtain $a_{B,y}^{max}$ for the entirety of the curve.
As a result, many of the curves will have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.

@@

\begin{figure}[thpb]
  \centering
  \begin{tabular}{cc}
  \subfigure[6-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/6phase_v(s).png}
  \label{fig:6phaseprofile}
  } &
  \subfigure[4-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4phase_v(s).png}
  \label{fig:4phaseprofile}
  } \\
  \subfigure[4 Reversed phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \label{fig:4rphaseprofile}
  } &
  \subfigure[3-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/3phase_v(s).png}
  \label{fig:3phaseprofile}
  }
  \end{tabular}
  \caption{6, 4, 4Reversed and 3-phase profiles, displayed as speed vs. position along path}

@@

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to look up $v_{B,x}(t_{veh})$, $a_{B,x}(t_{veh})$, and $j_{B,x}(t_{veh})$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, reference time as a function of vehicle position along the path, $t(s)$,F may be approximated as cubic if a spline is being constructed from knots which have a very high resolution.
In this case, an $s(t)$ spline has already been created using the control points from the unified planning process described in Section~\ref{sec:jerkprofiles}, and it is now resampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating the $t(s_{veh})$ then yields the current reference time.

@@

\textbf{RG: abrupt transition. need to summarize here}

@@

In this paper, we have presented a novel real-time method for planning longitudinal trajectories 
in an autonomous car to follow an urban path with online updates to avoid pedestrians on the roadway by slowing down or 
stopping. We built a robust stopping model as part of Trajectory Planner reliably integrated with 
the Path Manager.
We can travel along desired path, stop at stop signs, stop for pedestrians in roadway, and continue after 
they leave. Our system handles complex cases that were not explicitly programmed gracefully, such as following 
pedestrians if they continue walking on the road away from the car. Our system works with multiple 
pedestrians as we only need to consider the closest pedestrian ahead of us.

>>>>

We first describe the architecture of our system in Sec. \ref{sec:systemarchirecture}.
We also describe other subsystems that our system needs to work with, and planned stops.
Section \ref{sec:pathmanager} describes the high level Path Manager that calls the Trajectory Planner as necessary to 
exhibit reactive behavior and stop for pedestrians that appear on the road.
In Section \ref{sec:trajectoryplanning}, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies maximum velocity, acceleration and jerk constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
We then conclude and discuss future extensions.
% tracking

@@

We assume that we have access to a path planner.
For example, this can be a service similar to Google Maps except that instead of road level route, it provides lane level route. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a high resolution digital map with lane centers, stop signs, crosswalk geometry, and turning curves at intersections.
The destination is manually input into the system by the passengers.
Using the path planner, we obtain a path along lane centers from the vehicle's current location (computed by the navigation filter) to the destination.
This plan is then output as a set of global waypoints.

@@

Our High Resolution Map database is used to search for stop signs and provide their locations.
The plan waypoints corresponding to stop signs are then flagged for later processing.
We also have an In-Out Algorithm implemented via polygon intersection that can be used to ignore “safe” pedestrians
Pedestrians that are on sidewalks, off-path crosswalks, and behind planned stops as shown in Figure \ref{fig:intersect} can be considered ``safe'' and are ignored.
This is done by searching the same map database used for path planning.
Remaining pedestrians pose collision risk and the vehicle needs to reactively slow down or stop for them.
This is accomplished by sending stop message with pedestrian locations to the path manager.

@@

The task of Trajectory Planning is to take a 2 dimensional (horizontal plane) set of waypoints from the Path Manager, and compute a series of constant jerk intervals for motion along the length of the sub-path.
This trajectory must be time optimal yet still fall within constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

@@

The segmentation process proceeds as follows:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where $v_m$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
%$initial/final speeds, speed limit, peak acceleration and jerk 
are found for every point in the given subpath.
  \item \emph{Clustering}, in which subpath points are grouped sequentially and the segment boundaries are determined..
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described in Section \ref{sec:jerkprofiles} may be applied to each of the segments so that a plan of jerk vs. time may be generated.

@@

% need better notation here.
In the consolidation step, a single set of $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
%initial/final speeds, speed limit, peak acceleration and jerk 
must be calculated for each segment using the values corresponding to each of the waypoints which comprise the segment in question.
The minimum of scalar across all constituent points is chosen.
While not time optimal, it does ensure that no constraints are violated while still keeping the number of total segments low.
In the present example, this means that in the straight portions of the subpath $v_m = SL$ and in the curves $v_m$ is set to the value required to obtain $a_{B,y}^{max}$ for the entirety of the curve.
As a result, many of the curves will have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.

@@

\begin{figure}[thpb]
  \centering
  \begin{tabular}{cc}
  \subfigure[6-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/6phase_v(s).png}
  \label{fig:6phaseprofile}
  } &
  \subfigure[4-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4phase_v(s).png}
  \label{fig:4phaseprofile}
  } \\
  \subfigure[Reversed 4-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \label{fig:4rphaseprofile}
  } &
  \subfigure[3-phase profile] {
  \includegraphics[width=0.4\columnwidth]{graphics/3phase_v(s).png}
  \label{fig:3phaseprofile}
  }
  \end{tabular}
  \caption{6, 4, Reversed 4 and 3-phase profiles, displayed as speed vs. position along path}

@@

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to look up $v_{B,x}(t_{veh})$, $a_{B,x}(t_{veh})$, and $j_{B,x}(t_{veh})$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, reference time as a function of vehicle position along the path, $t(s)$, F may be approximated \textbf {as cubic if a spline ??????? } is being constructed from knots which have a very high resolution.
In this case, an $s(t)$ spline has already been created using the control points from the unified planning process described in Section~\ref{sec:jerkprofiles}, and it is now resampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating the $t(s_{veh})$ then yields the current reference time.

@@

To summarize, in the last three sections we have described how a urban path is broken into sub-paths,
and computation of a velocity and jerk profile for segments within sub-paths that honor constraints
for speed, velocity and acceleration as well as reactively slow down or stop for pedestrians on
the urban path.

@@

In this paper, we have presented a novel real-time method for planning longitudinal trajectories 
in an autonomous car to follow an urban path with online updates to avoid pedestrians on the roadway by slowing down or 
stopping. We built a robust stopping model as part of Trajectory Planner reliably integrated with 
the Path Manager.
We can travel along desired path, stop at stop signs, stop for pedestrians in roadway, and continue after 
they leave. Our system handles complex cases that were not explicitly programmed, gracefully, such as following 
pedestrians if they continue walking on the road away from the car. Our system works with multiple 
pedestrians as we only need to consider the closest pedestrian ahead of us.
